Automated Formal Synthesis\\ of Safe Digital Controllers for Continuous Plants

### 2018-05-16 automatica/paper.tex
added description about EG2
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\item[EG2] \textbf{(Sanity check)} Confirm the stability and safety of the synthesized controllers outside 
of our model representation using MATLAB. \note{Where is this done?}

@@

@@

\textit{Benchmark selection:} We report an assessment of both our approaches
over a diverse set of real-world benchmarks.  Nevertheless, this set of
benchmarks is limited within the scope of this paper and the performance may
not generalize to other benchmarks.\note{is this where we attempt asserting EG2?}

@@

\note{So, what about EG2? Shall we assert it? }

>>>>

\item[EG2] \textbf{(Sanity check)} Confirm the stability and safety of the synthesized controllers outside 
of our model representation using MATLAB. 
%\note{Where is this done?}

@@

\textcolor{blue}{The synthesized controllers are confirmed to be safe outside of our model
representation using MATLAB, achieving EG2.  A~link to the full
experimental environment, including scripts to reproduce the results, all
benchmarks and the tool, is provided in the
footnote as an Open Virtual Appliance (OVA).\footnote{\url{XXXX}}
The provided experimental environment runs multiple discretisations for each
benchmark, and lists the fastest as the result synthesis time.}

@@

\textit{Benchmark selection:} We report an assessment of both our approaches
over a diverse set of real-world benchmarks.  Nevertheless, this set of
benchmarks is limited within the scope of this paper and the performance may
not generalize to other benchmarks.
%\note{is this where we attempt asserting EG2?}

@@

%\note{So, what about EG2? Shall we assert it? }
